\documentclass[10pt,draftclsnofoot,onecolumn,journal,compsoc]{IEEEtran}
% for IEEEtran usage, see http://www.texdoc.net/texmf-dist/doc/latex/IEEEtran/IEEEtran_HOWTO.pdf

\usepackage[margin=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{pgfgantt}

\renewcommand{\linespread}{1.0}

\title{COAL: Coal and Open-pit surface mining impacts on American Lands}
\author{
  \IEEEauthorblockN{Taylor Alexander Brown, Heidi Ann Clayton, and Xiaomei Wang} \\
  \IEEEauthorblockA{CS 461: Senior Capstone Fall 2016 \\ Oregon State University}
}
\date{}

\IEEEtitleabstractindextext{
  \begin{abstract}
	Mining is known to cause environmental degradation, but software tools to identify mining impacts are lacking. Researchers studying this problem possess large imaging spectroscopy and environmental quality data sets as well as high-performance cloud-computing resources. This project provides a suite of algorithms using these data and resources to identify signatures of mining and correlate them with environmental impacts over time.
  \end{abstract}
}

\begin{document}

\maketitle
\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\newpage

\tableofcontents

\newpage

\section{Introduction}
Our team name for this project is ``COAL'': Coal and Open-pit surface mining impacts on American Lands.

\subsection{Purpose}
The purpose of this document is to describe what COAL will provide as a piece of software. This document will touch on the interfaces, features, and constraints of COAL. This document is intended for developers, potential users of COAL, and any stakeholders in projects that will make use of or reference COAL.

\subsection{Scope}
COAL will be a suite of algorithms that identifies, classifies, and quantifies the effects of open-pit mining on the surrounding environment. This will be done by first using spectroscopy data to identify mining activity and then using data provided by GRaND to attempt to correlate these identified sites with environmental impacts over time. These algorithms will be provided as reusable components that can be used in cloud-based systems such as NASA Ames Stereo Pipeline. There will also be a website that will present the algorithms and related data visualization as well as links to the source code, project wiki, API documentation, and developer profiles to anyone interested in using COAL for their cloud-based platform or research.

\subsection{Definitions, acronyms, and abbreviations}
\begin{description}[\IEEEsetlabelwidth{NASA Ames Stereo Pipeline}]
\item[AGU] American Geophysical Union
\item[API] Application Programming Interface
\item[AVIRIS] Airborne Visible/Infrared Imaging Spectrometer
\item[COAL] Coal and Open-pit surface mining impacts on American Lands
\item[GRaND] Global Reservoir and Dam Database
\item[Imaging Spectroscopy] ``[A]cquisition of images where for each spatial resolution element in the image a spectrum of the energy arriving at the sensor is measured [1].''
\item[LSE] Land and Solid Earth
\item[MTM] Mountain-top Mining
\item[NASA Ames Stereo Pipeline] A cloud-based platform that provides tools for processing stereo imagery from satellites, rovers, aerial photography, and historical images [2].
\end{description}

\subsection{References}

\begin{enumerate}[ {[}1{]} ]
\item "Imaging spectroscopy," in Jet Propulsion Laboratory, 2007. [Online]. Available: \url{http://aviris.jpl.nasa.gov/html/aviris.spectroscopy.html}. Accessed: Nov. 4, 2016.
\item "Neo-geography Toolkit," in National Aeronautics and Space Administration. [Online]. Available: \url{https://ti.arc.nasa.gov/tech/asr/intelligent-robotics/ngt/stereo/}. Accessed: Nov. 4, 2016.
\end{enumerate}

\subsection{Overview}
The rest of this document contains an overall description of the project, a list of specific requirements, and signatures from the client and students.

\section{Overall description}

\subsection{Product perspective}
The COAL suite of algorithms will be compatible with cloud-based platforms. Users will interact with COAL's homepage in order to view a detailed analysis of COAL's algorithms and data visualization using spectroscopy and mineral maps. COAL's algorithms and data analysis will be interfaced with Python data analysis and visualization libraries. COAL's algorithms will have time and space complexity that is efficient enough for users to process very large data sets (e.g. 5+ GB). There are no hardware components to this product nor are there communications interfaces.

\subsection{Product functions}
Analyze imaging spectroscopy and environmental quality data sets to generate human-readable reports and visualizations. Provide API documentation, wiki, homepage, source code, and research to allow others to use, improve, and replicate this work.

\subsection{User characteristics}
The intended users are data scientists at research institutions. Users are expected to have access to image spectroscopy and environmental quality data sets which they wish to study. Users are also expected to have access to high-performance cloud computing resources and experience deploying applications to them. In general, the intended users are highly educated, experienced, and technical, but not necessarily proficient in programming.

\subsection{Constraints}
COAL will be efficient enough to process large data sets on high-performance cloud servers in a practical amount of time for research applications.

\subsection{Assumptions and dependencies}
The system requirements (such as operating system, build environment, and programming language interpreter version) are to be determined based on the requirements of the third-party libraries chosen to implement it.

\section{Specific Requirements}

\subsection{Research background literature and libraries}
On an ongoing basis for the duration of the project, review background literature and libraries and provide relevant references in project documentation. Literature may include videos, books, websites, and journal articles. Libraries include third-party software modules used and any new versions and functionalities that are added to them.

\subsection{Problem statement}
Provide documents that define the scope of the software suite from both the client perspective and the student perspective. The client problem statement provides a high-level overview of the client's goals for the project. The student problem statement describes the project from a computer science perspective, giving an overview of the problem domain and the steps taken to solve it.

\subsection{Requirements document}
Provide a document that describes in detail what tasks are to be completed and when.

\subsection{Develop Software}
Develop a suite of imagery processing algorithms using existing libraries and, if necessary, custom code. The behavior of each algorithm should be verified with automated tests. The algorithms should be efficient enough and effective enough for data scientists to justify adopting and deploying them to solve real-world problems. The results should include visualizations that allow data scientists to infer meaningful relationships from the data sets.

\subsubsection{Mineral identification and classification}
Implement algorithms to identify and classify minerals and their spatial relationships from imaging spectroscopy data.

\subsubsection{Identify mining}
Implement algorithms to identify regions of mining activity from the mineral identification and classification data.

\subsubsection{Correlate mining with environmental impact}
Implement algorithms to correlate the regions of mining activity with data on regions of environmental degradation.

\subsubsection{Rank and document changes over time}
Implement algorithms to derive spatial and temporal relationships between the regions of mining activity and the regions of environmental degradation.

\subsection{API documentation}
Provide API documentation for developers in a human-readable format that is automatically generated from the codebase.

\subsection{Wiki}
Provide a wiki with documentation for end users containing comprehensive usage instructions and relevant background information. Also provide a development blog with weekly updates from the development team.

\subsection{Homepage}
Provide a website that serves as the project homepage. The homepage should describe the project in general terms and demonstrate example imagery and data. Links to relevant sites including the source code repository, API documentation, Wiki, and developer profiles should be included. It should be accessible, interactive, and self-contained.

\subsection{Release Software}
Release the software as a collection of reusable modules which data scientists may deploy to cloud platforms. All code is to be released under the Apache License, Version 2.0.

\subsection{Publish Research Paper}
Publish a research paper and present it to a scientific society such as the AGU. The paper should explain the research problem, describe the software developed to solve it, and present as a case study an analysis of imagery from the AVIRIS project.

% academic calendar: http://catalog.oregonstate.edu/ChapterDetail.aspx?key=148
% engineering calendar: http://eecs.oregonstate.edu/industry-relations/calendar
% course timeline: http://eecs.oregonstate.edu/capstone/cs/capstone.cgi?home=1

\newcommand{\firstdayoffallterm}{2016-09-21}      % first day of fall term
\newcommand{\startday}{2016-10-02}                % day groups assigned
\newcommand{\fallprogressreportdue}{2016-12-05}   % finals week of fall term
\newcommand{\alphareleasedue}{2017-02-13}         % week 6 of winter term
\newcommand{\betareleasedue}{2017-03-20}          % finals week of winter term
\newcommand{\winterprogressreportdue}{2017-03-20} % finals week of winter term
\newcommand{\releasedue}{2017-05-15}              % monday prior to tentative expo date
\newcommand{\expoday}{2017-05-19}                 % tentative expo date
\newcommand{\finalreportdue}{2017-06-12}          % finals week of spring term
\newcommand{\lastdayofspringterm}{2017-06-16}     % last day of spring term

\begin{figure}

  % gantt chart: http://mirrors.rit.edu/CTAN/graphics/pgf/contrib/pgfgantt/pgfgantt.pdf
  \begin{ganttchart}[x unit=0.15em, time slot format=isodate, link bulge=4]{\firstdayoffallterm}{\lastdayofspringterm}

    % gantt chart title
    \gantttitlecalendar{year, month=shortname} \\

    % gantt chart bars
    \ganttbar{Research literature and libraries}{\startday}{\expoday} \\
    \ganttbar[name=problem]{Problem Statement}{\startday}{2016-10-26} \\
    \ganttbar[name=requirements]{Requirements Document}{2016-10-26}{2016-11-04} \\
    \ganttbar[name=mineralid]{Mineral Identification}{\fallprogressreportdue}{\alphareleasedue} \\
    \ganttbar[name=miningid]{Identify Mining}{\alphareleasedue}{\betareleasedue} \\
    \ganttbar[name=impact]{Correlate Impact}{\betareleasedue}{\releasedue} \\
    \ganttbar[name=changes]{Document Changes}{\betareleasedue}{\releasedue} \\
    \ganttbar{API Documentation}{\fallprogressreportdue}{\releasedue} \\
    \ganttbar{Wiki}{\fallprogressreportdue}{\releasedue} \\
    \ganttbar{Homepage}{\betareleasedue}{\finalreportdue} \\
    \ganttbar{Release Software}{\releasedue}{\finalreportdue} \\
    \ganttbar{Publish Research Paper}{\releasedue}{\finalreportdue}

    % gantt chart links
    \ganttlink{problem}{requirements}
    \ganttlink{mineralid}{miningid}
    \ganttlink{miningid}{impact}
    \ganttlink[link mid=0.25]{miningid}{changes}

  \end{ganttchart}

  \caption{Gantt Chart: Timeline of Project Tasks}

\end{figure}

\end{document}
